---
title: "Darwin Core Mappin Vliegend hert"
author: "Dimitri Brosens"
output: html_document
date: "`r Sys.Date()`"

---

# Setup 

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = TRUE)
```

Load libraries:

```{r message = FALSE}
library(tidyverse)      # To do data science
library(tidylog)        # To provide feedback on dplyr functions
library(magrittr)       # To use %<>% pipes
library(here)           # To find files
library(janitor)        # To clean input data
library(readxl)         # To read Excel files
library(rgbif)          # To use GBIF services
library(uuid)           # To generate UUID's
#library(rlang)          # to generate hash
library(digest)
```

# Read source data



```{r}
input_data_dep <- read_delim(here::here("datasets","meetnetten-vliegendhert_temp","data","interim","transectobservationsGBIF_refined.csv"), ",")

input_data <- read_excel (here::here("datasets","meetnetten-vliegendhert_temp","data","raw","transectobservationsGBIF.xlsx"))

```


Preview data:

```{r}
input_data %>% head()
```



# Preprocessing

## Tidy data

Clean data somewhat:

```{r}
input_data %<>% 
  remove_empty("rows") %<>%
  clean_names()
```




### fix unique ID issue

```{r}
input_data <- mutate_all(input_data, as.character())
```


  # Darwin Core mapping

Map the data to [Darwin Core Occurrence](http://rs.gbif.org/core/dwc_occurrence_2015-07-02.xml).

```{r}
occurrence <- input_data
```

### type

```{r}
occurrence %<>% mutate(dwc_type = "Event")
```

### language

```{r}
occurrence %<>% mutate(dwc_language = "en")
```

### license

```{r}
occurrence %<>% mutate(dwc_license = "http://creativecommons.org/publicdomain/zero/1.0/")
```

### rightsHolder

```{r}
occurrence %<>% mutate(dwc_rightsHolder = recode (visit_location_country
                                                 , "Belgium" = "INBO"
                                                 , "Spain" = "Rey Juan Carlos University"
                                                 , "The Netherlands" = "Naturalis Biodiversity Center"
                                                 , "Croatia" = "University of Zagreb"
                                                 , "Germany" = "Hirschkäferfreunde-Nature"
                                                 , "Poland" = "University of Wroclaw"
                                                 , "Serbia" = "Serbia"
                                                 , "Slovenia" = "National Institute of Biology"
                                                 , "Switzerland" = "Independent researcher"
                                                 , "United Kingdom" = "Royal Holloway University of London"
                                                 , "Portugal" = "CIBIO/InBIO"
                                                 , "Italy" = "University of Florence" ))
```





### accessRights

```{r}
occurrence %<>% mutate(dwc_accessRights = "http://www.inbo.be/en/norms-for-data-use") 
```

### datasetID

```{r}
occurrence %<>% mutate(dwc_datasetID = "")
```

### institutionCode


```{r}
occurrence %<>% mutate(dwc_institutionCode = recode (visit_location_country
                                                 , "Belgium" = "INBO"
                                                 , "Spain" = "Rey Juan Carlos University"
                                                 , "The Netherlands" = "Naturalis Biodiversity Center"
                                                 , "Croatia" = "University of Zagreb"
                                                 , "Germany" = "Hirschkäferfreunde-Nature"
                                                 , "Poland" = "University of Wroclaw"
                                                 , "Serbia" = "Serbia"
                                                 , "Slovenia" = "National Institute of Biology"
                                                 , "Switzerland" = "Independent researcher"
                                                 , "United Kingdom" = "Royal Holloway University of London"
                                                 , "Portugal" = "CIBIO/InBIO"
                                                 , "Italy" = "University of Florence" ))
```


### datasetName

```{r}
occurrence %<>% mutate(dwc_datasetName = "European stag beetle monitoring network: transect observations")
```

### basisOfRecord

```{r}
occurrence %<>% mutate(dwc_basisOfRecord = "HumanObservation")
```

### occurrenceID


```{r}
occurrence %<>% mutate(dwc_occurrenceID = str_c("INBO:VG:tr:", visit_id ,":" , row_number()))




  
```




### recordedBy

```{r}
occurrence %<>% 
  mutate(dwc_recordedBy = purrr::map_chr(visit_user_name, ~digest(.x, algo = "md5")))
```


```{r}
vdigest <- Vectorize(digest) 
occurrence %<>% mutate(dwc_recordedBy3 = vdigest(visit_user_name, algo = "md5"))
```


### individualCount

```{r}
#mutate(occurrence$mm)as.numeric()
  
occurrence %<>% mutate(dwc_individualCount = number)

```




### occurrenceStatus

```{r}
occurrence %<>% mutate(dwc_occurrenceStatus = 'present')
```



### eventID

```{r}
occurrence %<>% mutate(dwc_eventID = str_c("INBO:VH:EV:" , visit_id))
```

### eventDate

```{r}
occurrence %<>% mutate(dwc_eventDate = visit_start_date)
```




### habitat



### samplingProtocol

```{r}
occurrence %<>% mutate(dwc_samplingProtocol = visit_protocol) 
```
### sex

```{r}
occurrence %<>% mutate(dwc_sex = tolower(sex))
```

### lifeStage

```{r}
occurrence %<>% mutate(dwc_lifeStage = life_stage)


```
### occurrenceRemarks

```{r}
occurrence %<>% mutate(dwc_occurrenceRemarks = activity)


```

### locality

```{r}
occurrence %<>% mutate(dwc_locality = location)

```


### continent

```{r}
occurrence %<>% mutate(dwc_continent = "Europe")
```

### countryCode

```{r}
occurrence %<>% mutate(dwc_countryCode = recode (visit_location_country
                                                 , "Belgium" = "BE"
                                                 , "Spain" = "ES"
                                                 , "The Netherlands" = "NL"
                                                 , "Croatia" = "HR"
                                                 , "Germany" = "DE"
                                                 , "Poland" = "PL"
                                                 , "Serbia" = "RS"
                                                 , "Slovenia" = "SI"
                                                 , "Switzerland" = "CH"
                                                 , "United Kingdom" = "GB"
                                                 , "Portugal" = "PT"
                                                 , "Italy" = "IT" ))
```


### locationRemarks



### decimalLatitude

```{r}
occurrence %<>% mutate(dwc_decimalLatitude = sprintf(
  "%.5f",
  round(lat, digits = 5) 
))
```



### decimalLongitude

```{r}
occurrence %<>% mutate(dwc_decimalLongitude = sprintf(
  "%.5f",
  round(lng, digits = 5)
))
```

### geodeticDatum

```{r}
occurrence %<>% mutate(dwc_geodeticDatum = "WGS84") 
```

### coordinateUncertaintyInMeters

```{r}
occurrence %<>% mutate(dwc_coordinateUncertaintyInMeters = "250")
```
### Identification
vdigest <- Vectorize(digest) 


```{r}

occurrence %<>% mutate(dwc_identifiedBy = paste(vdigest(visit_user_name, algo = "md5")))
```

```{r}
#occurrence %<>% mutate(dwc_identifiedByID = "https://orcid.org/0000-0001-5198-5928")
```


```{r}
#occurrence %<>% mutate(dwc_dateIdentified = identified_date)
```




### scientificName

### scientificName

```{r}
occurrence %<>% mutate(dwc_scientificName = scientific_name)

```


```{r}
occurrence %<>% filter(!is.na(dwc_scientificName))

#df %>% filter(!is.na(col1))
```


### kingdom

```{r}
occurrence %<>% mutate(dwc_kingdom = "Animalia")
```

### vernacularName


### taxonRank

```{r}
occurrence %<>% mutate(dwc_taxonRank = "species")
```

### nomenclaturalCode

```{r}
occurrence %<>% mutate(dwc_nomenclaturalCode = "ICZN")
```

## Post-processing

```{r}
occurrence %<>% select(starts_with("dwc_"))
colnames(occurrence) <- str_remove(colnames(occurrence), "dwc_")
```

```{r}
occurrence <- mutate_all(occurrence, as.character())
```

```{r}
occurrence$eventDate <- str_replace_all(occurrence$eventDate, "NA", "")
```

```{r}
occurrence %>% 
  mutate(across(where(is.character), str_trim))
```


```{r}
#occurrence <-  mutate_at(c(occurrence$eventDate), ~replace_na(.,""))

```



```{r}
#occurrence %<>% distinct(occurrenceID2, .keep_all = TRUE)
```

Preview data:

```{r}
occurrence %>% head()
```

Save to CSV:

```{r}
write_delim (occurrence, here::here("datasets","meetnetten-vliegendhert_temp","data","processed","occurrence.csv"),delim = ',', na = "")

```

# Checks

```{r}
test <- length(unique(occurrence$eventID))
test2 <- length(unique(occurrence$occurrenceID))

n_occur <- data.frame(table(occurrence$occurrenceID))

```


